---
title: "phia_interview_jsg"
author: "Jared Garfinkel"
date: "7/14/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = FALSE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
odk <- read_csv("./data/ODK.csv") %>% 
  janitor::clean_names() %>% 
  mutate(ptid = coalesce(ptide, ptidb)) %>% 
  select(ptid, confagey, confgend) %>% 
  mutate(ptid = str_trunc(ptid, 6, "left", ""),
         ptid = as_factor(ptid))
```

```{r}
vl_dat <- read_csv("./data/vl_all_active.csv") %>% 
  janitor::clean_names() %>% 
  tibble() %>% 
  mutate("ptid" = str_trunc(ptid, 6, "left", ""),
         ptid = as_factor(ptid))
```

```{r}
full_dat <- full_join(odk, vl_dat, by = "ptid")
```
### Question 1

#### a)	How many participants have ODK data, but not data in vl_all_active, and vice versa? 

#### b)	How many participants are in both datasets?


There are `r nrow(full_dat)` rows by `r ncol(full_dat)` columns in the combined dataset. 

There are `r n_distinct(pull(full_dat, ptid))` unique identifiers.

```{r}
odk_uniq <- odk %>% 
  select(ptid) %>% 
  arrange()

vl_dat_uniq <- vl_dat %>% 
  select(ptid) %>% 
  unique() %>% 
  arrange()
```

Of these, `r setdiff(odk_uniq, vl_dat_uniq) %>% nrow()` participants can be found in the ODK dataset and not the vl_all_active dataset,

while `r setdiff(vl_dat_uniq, odk_uniq) %>% nrow()` participants can be found in the vl_all_active dataset and not the ODK dataset.

### Question 2

#### How many adults (age >= 18) have had a DNA PCR test that failed? How many adults had a DNA PCR test that was approved?

Among adults 18 years or older, `r full_dat %>% filter(confagey > 17, testtype == "PCR", approved == "approved") %>% nrow()` participants had a blood test that was approved.

Meanwhile, `r full_dat %>% filter(confagey > 17, testtype == "PCR", approved == "failure") %>% nrow()` adults had a blood test that failed.

Note that a participant was omitted from this analysis if their age was missing.

### Question 3

#### How many females who have ODK data have approved Viral Load Results (Plasma or DBS)?

```{r}
odk_full <- left_join(odk, vl_dat, by = "ptid")
```


There were `r odk_full %>% filter(confgend == 2, testtype %in% c("VL", "VL_DBS"), approved == "approved") %>% nrow()` females with approved Viral Load Results from plasma or DBS in the ODK dataset.

### Question 4

Please find a new dataset attached.

```{r}
odk_vl <- odk_full %>% 
  filter(testtype %in% c("VL", "VL_DBS"),
         approved == "approved") %>% 
  select(ptid, testtype, guspec, dateadded, result)

write.csv(odk_vl, "final_jsg.csv")
```




